Report

### 2021-05-13 Rmd/report.Rmd
Separate target and distractor fixations

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid")) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))
```

@@

# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(age_group, participant, fill = valid_participant, colour = valid_participant)) +
	facet_grid(lp~location, scales = "free") +
	geom_point(size = 3, shape = 4) +
	geom_line(aes(group = participant)) +
	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.title.y = element_blank(),
		  axis.text.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "sample_cohort.png"))
```

@@

```{r lps, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	filter(valid_participant) %>% 
	ggplot(aes(age, doe_2, colour = lp)) +
	facet_grid(test_language~location) +
	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
	geom_point(size = 3, alpha = 0.5) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 20, xmax = 22, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 24, xmax = 26, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 28, xmax = 32, ymin = -Inf, ymax = Inf) +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(labels = percent) +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(linetype = "dotted", colour = "grey"),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		axis.text.y = element_text(size = 10)
	) +
	ggsave(here("Figures", "lps.png"))
```

@@

## Preprocessing participant data

@@

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	mutate(age_group = as.factor(paste0(age_group, " mo"))) %>% 
	drop_na(lp) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

#### Cross-sectional

@@

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "none",
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

@@

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(age_group, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = interaction(participant, trial_type)), alpha = 0.5) +
	geom_violin(position = position_dodge(width = 0.5)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
	labs(x = "Age (months)", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

### Target fixations: Time course analysis

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

@@

@@

```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_point(alpha = 0.5) +
	geom_smooth(se = FALSE, method = "lm") +
	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		  legend.position = "top",
		  axis.text.x = element_text(size = 10)) +
	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
```

@@

gaze_time_vocab_d <- gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		time_bin = time_bin*100,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		),
		age_group = paste0(age_group, " months")
	) %>% 
	drop_na()

@@

>>>>

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "No valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))
```

@@

# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "No valid"
		)
	) %>% 
	ggplot(aes(age_group, participant, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~location, scales = "free") +
	geom_point(size = 3, shape = 4) +
	geom_line(aes(group = participant)) +
	labs(x = "Age (months)", y = "Language profile", fill = "Valid?", colour = "Valid?") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(axis.title.y = element_blank(),
		  axis.text.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "sample_cohort.png"))
```

@@

```{r lps, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	filter(valid_participant) %>% 
	ggplot(aes(age, doe_2, colour = lp)) +
	facet_wrap(location~test_language) +
	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
	geom_point(size = 3, alpha = 0.5) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 20, xmax = 22, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 24, xmax = 26, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 28, xmax = 32, ymin = -Inf, ymax = Inf) +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(labels = percent) +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(linetype = "dotted", colour = "grey"),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		axis.text.y = element_text(size = 10)
	) +
	ggsave(here("Figures", "lps.png"))
```

@@

@@

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	mutate(age_group = as.factor(paste0(age_group, " mo"))) %>% 
	drop_na(lp) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(location~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

#### Cross-sectional {.tab-set .tab-pills}

@@

##### Age group: 21 months

```{r gaze_trial_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group == "21 months") %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_21.png"))

@@

##### Age group: 25 months

```{r gaze_trial_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group == "25 months") %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_25.png"))
```

##### Age group: 30 months

```{r gaze_trial_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group == "30 months") %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_30.png"))

##### {-}

@@

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop_target = mean(prop_target),
		prop_distractor = mean(prop_distractor),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	ggplot(aes(age_group, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = interaction(participant, trial_type)), alpha = 0.5) +
	geom_violin(position = position_dodge(width = 0.5)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, aoi)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
	labs(x = "Age (months)", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

### Target fixations: Time course analysis {.tabset .tab-pills}

```{r gaze_time_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>%
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group=="21 months") %>% 
	group_by(time_bin, trial_type, lp, age_group, location) %>% 
	summarise(
		prop_target = mean(prop_target, na.rm = TRUE),
		prop_distractor = mean(prop_distractor, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = aoi, fill = aoi, shape = aoi)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = "mean_se", geom = "pointrange", size = 0.5, alpha = 0.5) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time_21.png"))

@@

```{r gaze_time_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>%
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group=="25 months") %>% 
	group_by(time_bin, trial_type, lp, age_group, location) %>% 
	summarise(
		prop_target = mean(prop_target, na.rm = TRUE),
		prop_distractor = mean(prop_distractor, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = aoi, fill = aoi, shape = aoi)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = "mean_se", geom = "pointrange", size = 0.5, alpha = 0.5) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time_25.png"))

```{r gaze_time_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>%
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group=="30 months") %>% 
	group_by(time_bin, trial_type, lp, age_group, location) %>% 
	summarise(
		prop_target = mean(prop_target, na.rm = TRUE),
		prop_distractor = mean(prop_distractor, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = aoi, fill = aoi, shape = aoi)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = "mean_se", geom = "pointrange", size = 0.5, alpha = 0.5) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time_30.png"))

#### {-}

@@

```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
	summarise(prop = mean(prop_target), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_point(alpha = 0.5) +
	geom_smooth(se = FALSE, method = "lm") +
	labs(
		x = "L1 vocabulary size",
		y = "Target looking / Total looking",
		colour = "Condition",
		fill = "Condition"
	) + 
	scale_colour_brewer(palette = "Set1") +
	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		  legend.position = "top",
		  axis.text.x = element_text(size = 10)) +
	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
```

@@

gaze_time_vocab_d <- gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop_target = mean(prop_target, na.rm = TRUE),
		prop_distractor = mean(prop_distractor, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	pivot_longer(c(prop_target, prop_distractor), names_to = "aoi", values_to = "prop") %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		time_bin = time_bin*100,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		),
		age_group = paste0(age_group, " months"),
		aoi = str_to_sentence(str_remove(aoi, "prop_"))
	) %>% 
	drop_na()

@@

#### Target fixations: 21 months

```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}

gaze_time_vocab_d %>% 
	filter(age_group == "21 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
	) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

#### Target fixations: 25 months

```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}

gaze_time_vocab_d %>% 
	filter(age_group == "25 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
	) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

#### Target fixations: 30 months

```{r gaze_time_vocab_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%"}
